---
title: "p8105_hw2_lc3391"
author: "Lu Chen"
date: "9/28/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

# Problem 1

## Read data by sheets, and clean the datasets
```{r}
trash_wheel = read_excel( "Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "Mr. Trash Wheel",
                         range = "A2:N338", na = "" ) %>% 
  janitor::clean_names() %>% 
  na.omit() %>% 
  mutate(sports_balls = as.integer(round(sports_balls, 0)))

p_2017 = read_excel( "Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "2017 Precipitation", 
                     range = "A2:B14", na = "") %>% 
  janitor::clean_names() %>% 
  mutate(year = 2017)

p_2018 = read_excel( "Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "2018 Precipitation",
                     range = "A2:B14", na = "") %>%  
  janitor::clean_names() %>% 
  mutate(year = 2018)

combined_p = left_join(p_2017, p_2018, by = c("month")) %>% 
  mutate(Month = month.name)

```
- There are `r nrow(trash_wheel)` observations in the dataset Trash Wheel, and one of the key variables is volumn. 
- The number of observations in Combined Precipitation is `r nrow(combined_p)`, and the number of precipitation is one of the key variable.
- The total precipitation rate in 2018 is `r sum(pull(p_2018, total))`, and the median number of sports balls in a dumpster in 2017 is `r median(pull(filter(trash_wheel, year == 2017), sports_balls))`.

# Problem 2
```{r}
pols_month = read_csv(file = "./fivethirtyeight_datasets/pols-month.csv") %>% 
  janitor::clean_names() %>% 
  separate(mon, into = c("year", "month", "day")) %>% 
  mutate(
    month = as.numeric(month),
    month = month.abb[month]
  )

snp = read_csv(file = "./fivethirtyeight_datasets/snp.csv") %>% 
  janitor::clean_names() %>% 
  separate(col = date, into = c("year", "month", "day")) %>% 
  arrange(as.integer((year), as.integer(month))) %>% 
  select(year, month, everything()) %>% 
   mutate(
        month = as.numeric(month),
        month = month.abb[month]
      )

unemployment = read_csv(file = "./fivethirtyeight_datasets/unemployment.csv") %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    jan:dec, names_to = "month", values_to = "value") %>% 
  mutate(year = as.character(year)) %>% 
  select(year, everything())

pols_snp = full_join(pols_month, snp, by = c("year","month"))
pols_snp_unem = full_join(pols_snp, unemployment, by = c("year","month"))

```

- The dataset `pols_month` contains statistics related to politics corresponding to specific month. 
- The dataset `snp` illustrates the S&P stock index on the associated date.
- The dataset `unemployment` contains the unemployment rate in specific year and month.
- The resulting dataset `pols_sup_unem` combines all three datasets mentioned above together. It has `r nrow(pols_snp_unem)` observations and contains `r ncol(pols_snp_unem)` variables. The year meansure ranges from 1947 to 2015. The key vairable is `value`.



# Problem 3
```{r fig.width=6, message = FALSE, warning=FALSE}
Pop_name = read_csv("Popular_Baby_Names.csv") %>% 
  janitor::clean_names() %>% 
  mutate(gender = str_to_upper(gender), ethnicity = str_to_upper(ethnicity),
         childs_first_name = str_to_upper(childs_first_name)) %>% 
  mutate(ethnicity = recode(
    ethnicity, "ASIAN AND PACI" = "ASIAN AND PACIFIC ISLANDER","BLACK NON HISP" = "BLACK NON HISPANIC",
               "WHITE NON HISP" = "WHITE NON HISPANIC")
    ) %>% 
  distinct()

Olivia = filter(Pop_name, gender == "FEMALE", childs_first_name == "OLIVIA") %>% 
  select(-gender, -childs_first_name, -count) %>%
  arrange(ethnicity, year_of_birth) %>% 
  pivot_wider(names_from = year_of_birth, values_from = rank) %>% 
  knitr::kable()

pop_male = filter(Pop_name, gender == "MALE", rank == 1) %>% 
  select(-gender, -rank, -count) %>% 
  arrange(ethnicity, year_of_birth, childs_first_name) %>% 
  pivot_wider(names_from = year_of_birth, values_from = childs_first_name) %>%
  knitr::kable()

filter(Pop_name, gender == "MALE", ethnicity == "WHITE NON HISPANIC", year_of_birth == 2016) %>% 
  ggplot(aes(x = rank, y = count)) + geom_point(alpha = 0.4)
```


