---
title: "p8105_hw2_lc3391"
author: "Lu Chen"
date: "9/28/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

# Problem 1

## Read data by sheets, and clean the datasets
```{r}
trash_wheel = read_excel( "Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "Mr. Trash Wheel",
                         range = "A2:N338", na = "" ) %>% 
  janitor::clean_names() %>% 
  na.omit() %>% 
  mutate(sports_balls = as.integer(round(sports_balls, 0)))

p_2017 = read_excel( "Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "2017 Precipitation", 
                     range = "A2:B14", na = "") %>% 
  janitor::clean_names() %>% 
  mutate(year = 2017)

p_2018 = read_excel( "Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "2018 Precipitation",
                     range = "A2:B14", na = "") %>%  
  janitor::clean_names() %>% 
  mutate(year = 2018)

combined_p = left_join(p_2017, p_2018, by = c("month")) %>% 
  mutate(Month = month.name)

```
- There are `r nrow(trash_wheel)` observations in the dataset Trash Wheel, and one of the key variables is volumn. 
- The number of observations in Combined Precipitation is `r nrow(combined_p)`, and the number of precipitation is one of the key variable.
- The total precipitation rate in 2018 is `r sum(pull(p_2018, total))`, and the median number of sports balls in a dumpster in 2017 is `r median(pull(filter(trash_wheel, year == 2017), sports_balls))`.
